Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-14 docs/paper/paper.tex
update: va_curves: fixes

In this set of experiments, we have analyzed the performance of the proposed ANN design. The first experiment involves training loss over the SPR dataset. In this experiment, we have trained the ANN model for up to 3000 epochs and reported the training loss in Figure \ref{chart:trainingmse}. According to this experiment, training our ANN architecture more than 2500 epochs does not yield any improvement. Therefore, the training epoch limit is set to 2500 in all subsequent experiments. However, this number depends on the dataset and additional training may improve the results. Additionally, the benefit of augmented samples from the GAN phase is evident even at the training as they reduce the oscillations in the training loss.

@@

@@

		\end{axis}
		\end{tikzpicture}
		\caption{Configuration estimation on SPR dataset.}
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
		\end{axis}
		\end{tikzpicture}
		\caption{Configuration estimation on SPR dataset}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}

>>>>

In this set of experiments, we have analyzed the performance of the proposed ANN design. The first experiment involves training loss over the SPR dataset. In this experiment, we have trained the ANN model for up to 3000 epochs and reported the training loss in Figure \ref{chart:trainingmse}. According to this experiment, training our ANN architecture more than 2500 epochs does not yield any improvement. Therefore, the training epoch limit is set to 2500 in all subsequent experiments. However, this number depends on the dataset and additional training may improve the results. Additionally, the benefit of augmented samples from the GAN phase is evident even at the training as they reduce the \hl{fluctuations in the training loss and validation MSE}.

@@

\begin{figure}
	\begin{subfigure}{.48\textwidth}
		\centering
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=Epochs, 
		ylabel=Validation \space MSE,
		width=\textwidth,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		ymax=3,
		height=6cm,
		no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/va_loss_3k_our_data_without.txt};
		\addlegendentry{Without GAN}

		\addplot[line width=1pt,solid,color=red] %
		table{data/va_loss_3k_our_data_with.txt};
		\addlegendentry{With GAN}
		\end{axis}
		\end{tikzpicture}
	\end{subfigure}

	\caption{\hl{Validation MSE of the ANN model}}
	\label{chart:validationmse}
\end{figure}

@@

		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset.
		\\\hl{$ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{ $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}		
		  }
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset. 
		\\ \hl{$n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{$n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.} 
		}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}
